A lottery model of density-dependent selection

### 2017-10-14 manuscript.tex
latest

@@

Starting with Kostitzin's

@@

Yet selection does not only change relative genotypic proportions. Ultimately, it involves the births and deaths of individuals, and is therefore intimately connected to changes in absolute abundance \cite{evolution_demography_stuff}. This immediately poses a challenge: any description of evolution grounded in abundances needs to specify how population density is regulated, as well as how fitness depends on density, which may differ between genotypes (density-dependent selection). As a result,

One of the simplest and most widely used models of selection is to assign genotypes constant selection coefficients describing how their relative proportions change over time. This model is common in population genetics, where its simplicity is useful for analyzing the detailed time course of genotypic frequencies.

>>>>

In a huge class of evolutionary models, and in many introductory texts, selection is described in terms of shifts in genotypic frequencies (e.g. \cite[pp. 468]{barton_2007}). Genotypes are assigned constant selection coefficients describing how their relative proportions change over time. These selective shifts in frequency result from two fundamentally different population processes: i) in the absence of interactions between individuals, genotypic growth rates differ; ii) as a result of competitive interactions between individuals, some genotypes displace others. Population density is the key factor that controls whether individuals interact, thus controlling the relative contributions of these forms of selection.

The distinction between these forms of selection was perceived long ago by Kostitzin \citep{kostitzin_1939,christiansen_2004}, but is mostly associated with MacArthur's $r$/$K$ scheme \citep{macarthur_1962,macarthur_1967} and the following literature on density-dependent selection.

@@

@@

 This immediately poses a challenge: any description of evolution grounded in abundances needs to specify how population density is regulated, as well as how fitness depends on density, which may differ between genotypes (density-dependent selection). As a result,
